The impact of gas bulk rotation on the Lyman $\alpha$ line

### 2014-05-22 paper/ms.tex
paragraph on verhamme

Gas bulk rotation has a noticeable effect on the morphology of the
 \ly line. In this section we discuss the implications of these
 findings for the interpretation of available observational data.

>>>>

Gas bulk rotation has a noticeable effect on the morphology of the
 \ly line. In this section we compare our findings to other
 computational results and discuss the implications of these finding
 in the interpretation of observational data.

\cite{Verhamme12} studied \lya using two high resolution simulations
of individual galaxies. The main purpose of the study was to asses the
impact of two different InterStellar Medium (ISM) prescriptions. However, each simulated
galaxy had a disc structure with a clear rotation pattern in the ISM
and inflowing gas int the circum-galactic region. The configuration
had an axial symmetry and they reported a strong dependence of the
escape fraction and the total line intensity as a function of the
$\theta$ angle. In our results, none of these two quantities has a
dependence either on the inclination angle or the rotational
velocity. Therefore, the effect reported by \cite{Verhamme} is
consistent to the different hydrogen optical depth for different
viewing angles and not as an effect of the bulk rotation.
